Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
removed comment with the old FTLR
added color to FTLR condition

% \begin{theorem}[FTLR]
%   \label{thm:ftlr}
%   \[
%     \begin{array}{l}
%       \forall n,W,W_D,W_C,\perm_C,\perm_D,\lin_C,\lin_D,\baddr_C,\baddr_D,\eaddr_C,\eaddr_D,\aaddr_C,\aaddr_D \ldotp \\
%       \quad \left(
%       \begin{array}{l}
%         W = W_D \oplus W_C \wedge \\
%         \perm_D \in \readAllowed{} \Rightarrow \npair{(\baddr_D,\eaddr_D)} \in \readCond{\lin_D,W_D} \wedge\\
%         \perm_D \in \writeAllowed{} \Rightarrow\npair{(\baddr_D,\eaddr_D)} \in \writeCond{\lin_D,W_D} \wedge\\
%         \perm_D \notin \{\rwx,\rx\} \wedge \\
%         \perm_C = \rx \wedge\\
%         \npair{(\baddr_C,\eaddr_C)} \in \readCond{\lin_C,W_C}
%       \end{array}
%       \right)\\
%       \quad\Rightarrow 
%       \npair{\left(\arraycolsep=0pt\array{l}((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D),\\
%                       ((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D)\endarray \right)} \in \lre(W)

%     \end{array}
%   \]
% \end{theorem}

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
% Note: the below FTLR is simpler than the above thanks to the new expression relation relating pairs of caps rather than pairs of pairs of caps. It expresses that any reasonable executable capability is safe to use as the pc capability. 
\begin{theorem}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If
  \begin{itemize}
  \item $\npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{itemize}
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \trusted$

    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \[
        \sigrets = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\sigrets',\_} \wedge \sigma \in \sigrets'  \wedge \ta' \subseteq \ta\}
      \]
      and
      \[
        \sigcloss = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\_,\sigcloss'} \wedge \sigma \in \sigcloss'  \wedge \ta' \subseteq \ta\}
      \]
      \begin{itemize}           
\item $\Phi$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
  \item $\Phi$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
  \item $\Phi$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
  \item $\Phi$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{itemize}
  Then
  \[
    \npair{\left(\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \in \lreg{\trust}(W)
  \]
  \dominique{6-3-2018: I added $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
  \begin{definition}[The compilation assumptions]
    No call uses $\rtmp{1}$ for jumping.\\
    ...
  \end{definition}

>>>>

\begin{theorem}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If
  \begin{itemize}
  \item $\npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{itemize}
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \trusted$
    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \[
        \sigrets = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\sigrets',\_} \wedge \sigma \in \sigrets'  \wedge \ta' \subseteq \ta\}
      \]
      and
      \[
        \sigcloss = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\_,\sigcloss'} \wedge \sigma \in \sigcloss'  \wedge \ta' \subseteq \ta\}
      \]
      \begin{itemize}           
\item $\src{\Phi}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
  \item $\src{\Phi}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
  \item $\src{\Phi}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
  \item $\src{\Phi}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{itemize}
  Then
  \[
    \npair{\left(\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \in \lreg{\trust}(W)
  \]
  \dominique{6-3-2018: I added $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
  \begin{definition}[The compilation assumptions]
    No call uses $\rtmp{1}$ for jumping.\\
    ...
  \end{definition}
